A spatial analysis of the environmental correlates of COVID-19 incidence in Spain

### 2020-04-18 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.Rmd
Successfully embeded math in README.md

```{r descriptive-statistics, echo=FALSE}
data.frame(Variable = c("COVID-19 Incidence",
                        "GDPpc", 
                        "Older", 
                        "Population Density",
                        "Mean Temperature",
                        "Humidity"),
           Note = c("Incidence in reported cases of SARS-19 per 100,000 people",
                    "GDP per capita in €1,000s",
                    "Percentage of people aged 65 and older in the province",
                    "Population density in the province in people per sq.km",
                    "Mean temperature in province by date, in C",
                    "Relative humidity in province by date"),
           Min = c(min(covid19_spain$Incidence),
                   min(provinces_spain$GDPpc),
                   min(provinces_spain$Older),
                   min(provinces_spain$Density),
                   min(covid19_spain$Mean_Temp),
                   min(covid19_spain$Humidity)),
           Mean = c(mean(covid19_spain$Incidence),
                   mean(provinces_spain$GDPpc),
                   mean(provinces_spain$Older),
                   mean(provinces_spain$Density),
                   mean(covid19_spain$Mean_Temp),
                   mean(covid19_spain$Humidity)),
           Max = c(max(covid19_spain$Incidence),
                   max(provinces_spain$GDPpc),
                   max(provinces_spain$Older),
                   max(provinces_spain$Density),
                   max(covid19_spain$Mean_Temp),
                   max(covid19_spain$Humidity)),
           SD = c(sd(covid19_spain$Incidence),
                   sd(provinces_spain$GDPpc),
                   sd(provinces_spain$Older),
                   sd(provinces_spain$Density),
                   sd(covid19_spain$Mean_Temp),
                   sd(covid19_spain$Humidity)),
           Source = c("Montera34",
                      "INE",
                      "INE",
                      "INE",
                      "AEMET",
                      "MAPA")) %>%
  kable("latex",
        booktabs = TRUE,
        digits = 2,
        caption = "\\label{tab:descriptive-statistics}Descriptive statistics") %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(7, width = "5em") %>%
  footnote(general = c("Montera34: https://code.montera34.com:4443/numeroteca/covid19/-/blob/master/README_providencialdata19.md", 
                       "INE (Instituto Nacional de Estadistica): https://www.ine.es/",
                       "AEMET (Agencia Estatal de Meteorologia): http://eportal.mapa.gob.es",
                       "MAPA (Ministerio de Agricultura, Pesca y Alimentacion): http://eportal.mapa.gob.es"))
```

@@

@@

@@

@@

@@

Summary of best model.
```{r summary-best-model, echo=FALSE}
data.frame(Coefficient = sur.slm_lag11$coefficients, 
                   pval = dnorm(abs(sur.slm_lag11$coefficients/sur.slm_lag11$rest.se))) %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Variable = c("Intercept", 
                      "log(GDPpc)", 
                      "log(Older)",
                      "log(Density)",
                      "Transit",
                      "log(Humidity)",
                      "log(Temperature)",
                      rep(c("Intercept",
                            "log(Density)", 
                            "Transit", 
                            "log(Humidity)", 
                            "log(Temperature)"), 29)),
         Variable = factor(Variable, 
                           levels = c("Intercept", 
                                      "log(GDPpc)", 
                                      "log(Older)", 
                                      "log(Density)",
                                      "Transit", 
                                      "log(Humidity)",
                                      "log(Temperature)"))) %>%
  group_by(Variable) %>%
  summarize(Min = min(Coefficient), 
            Mean = mean(Coefficient), 
            Max = max(Coefficient),
            pns = sum(pval > 0.10), # Number of coefficients with p > 0.1
            p10 = sum(pval <= 0.10) - sum(pval <= 0.05), # Number of coefficients with  0.1 <= pval < 0.05
            p05 = sum(pval <= 0.05)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Non-constrained", 
                  "Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")) %>%
  kable("latex",
        booktabs = TRUE,
        digits = 3,
        col.names = c("Variable", "Min", "Mean", "Max", "p > 0.10", "0.10 <= p < 0.05", "p <= 0.05", "Note"),
        caption = "\\label{tab:summary-best-model}Summary of estimation results best model (lagged 11-day moving average)") %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_header_above(c(" " = 1, "Estimates" = 3, "Significance" = 3, " " = 1)) %>%
  footnote(general = c("Significance: This is the number of coefficients with p-values as indicated",
                       "Non-constrained: coefficient was allowed to vary across equations",
                       "Constrained: coefficient as constant across equations"))
```

>>>>

```{r descriptive-statistics, echo=FALSE}
data.frame(Variable = c("COVID-19 Incidence",
                        "GDPpc", 
                        "Older", 
                        "Population Density",
                        "Mean Temperature",
                        "Humidity"),
           Note = c("Incidence in reported cases of SARS-19 per 100,000 people",
                    "GDP per capita in €1,000s",
                    "Percentage of people aged 65 and older in the province",
                    "Population density in the province in people per sq.km",
                    "Mean temperature in province by date, in C",
                    "Relative humidity in province by date"),
           Min = c(min(covid19_spain$Incidence),
                   min(provinces_spain$GDPpc),
                   min(provinces_spain$Older),
                   min(provinces_spain$Density),
                   min(covid19_spain$Mean_Temp),
                   min(covid19_spain$Humidity)),
           Mean = c(mean(covid19_spain$Incidence),
                   mean(provinces_spain$GDPpc),
                   mean(provinces_spain$Older),
                   mean(provinces_spain$Density),
                   mean(covid19_spain$Mean_Temp),
                   mean(covid19_spain$Humidity)),
           Max = c(max(covid19_spain$Incidence),
                   max(provinces_spain$GDPpc),
                   max(provinces_spain$Older),
                   max(provinces_spain$Density),
                   max(covid19_spain$Mean_Temp),
                   max(covid19_spain$Humidity)),
           SD = c(sd(covid19_spain$Incidence),
                   sd(provinces_spain$GDPpc),
                   sd(provinces_spain$Older),
                   sd(provinces_spain$Density),
                   sd(covid19_spain$Mean_Temp),
                   sd(covid19_spain$Humidity)),
           Source = c("Montera34",
                      "INE",
                      "INE",
                      "INE",
                      "AEMET",
                      "MAPA")) %>%
  kable("latex",
        #"html",
        booktabs = TRUE,
        digits = 2,
        caption = "\\label{tab:descriptive-statistics}Descriptive statistics") %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  #kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(7, width = "5em") %>%
  footnote(general = c("Montera34: https://code.montera34.com:4443/numeroteca/covid19/-/blob/master/README_providencialdata19.md", 
                       "INE (Instituto Nacional de Estadistica): https://www.ine.es/",
                       "AEMET (Agencia Estatal de Meteorologia): http://eportal.mapa.gob.es",
                       "MAPA (Ministerio de Agricultura, Pesca y Alimentacion): http://eportal.mapa.gob.es"))
```

@@

<!--Equation for README.md generated using this app https://alexanderrodin.com/github-latex-markdown/-->
<!--
![\begin{equation} \label{eq:sur-sim} \begin{bmatrix} y_1 \\ y_2 \\ \vdots \\ y_T \end{bmatrix} = \begin{bmatrix} X_1 & 0 & \cdots & 0 \\ 0 & X_2 & \cdots & 0 \\ \vdots & \vdots & \ddots & \vdots \\ 0 & 0 & \cdots & X_T \end{bmatrix} \ \begin{bmatrix} \beta_1 \\ \beta_1 \\ \vdots \\ \beta_T \end{bmatrix} + \begin{bmatrix} \epsilon_1 \\ \epsilon_2 \\ \vdots \\ \epsilon_T \end{bmatrix} \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-sim%7D%20%5Cbegin%7Bbmatrix%7D%20y_1%20%5C%5C%20y_2%20%5C%5C%20%5Cvdots%20%5C%5C%20y_T%20%5Cend%7Bbmatrix%7D%20%3D%20%5Cbegin%7Bbmatrix%7D%20X_1%20%26%200%20%26%20%5Ccdots%20%26%200%20%5C%5C%200%20%26%20X_2%20%26%20%5Ccdots%20%26%200%20%5C%5C%20%5Cvdots%20%26%20%5Cvdots%20%26%20%5Cddots%20%26%20%5Cvdots%20%5C%5C%200%20%26%200%20%26%20%5Ccdots%20%26%20X_T%20%5Cend%7Bbmatrix%7D%20%5C%20%5Cbegin%7Bbmatrix%7D%20%5Cbeta_1%20%5C%5C%20%5Cbeta_1%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cbeta_T%20%5Cend%7Bbmatrix%7D%20%2B%20%5Cbegin%7Bbmatrix%7D%20%5Cepsilon_1%20%5C%5C%20%5Cepsilon_2%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cepsilon_T%20%5Cend%7Bbmatrix%7D%20%5Cend%7Bequation%7D)
-->

@@

<!--
![\begin{equation} \label{eq:sur-err} E\[\epsilon_t \epsilon'_{t'}\]=\sigma_{tt'} \end{equation} ](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-err%7D%20E%5B%5Cepsilon_t%20%5Cepsilon'_%7Bt'%7D%5D%3D%5Csigma_%7Btt'%7D%20%5Cend%7Bequation%7D%20)
-->

@@

<!--
![\begin{equation} y = X \beta + \epsilon \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20y%20%3D%20X%20%5Cbeta%20%2B%20%5Cepsilon%20%5Cend%7Bequation%7D)
-->

@@

<!--
![\begin{equation} \label{eq:sur-slm} \bf{A}y = X \beta + \epsilon \\ \epsilon =N(0,\Omega) \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-slm%7D%20%5Cbf%7BA%7Dy%20%3D%20X%20%5Cbeta%20%2B%20%5Cepsilon%20%5C%5C%20%5Cepsilon%20%3DN(0%2C%5COmega)%20%5Cend%7Bequation%7D)
-->

@@

Summary of best model.
```{r summary-best-model, echo=FALSE}
data.frame(Coefficient = sur.slm_lag11$coefficients, 
                   pval = dnorm(abs(sur.slm_lag11$coefficients/sur.slm_lag11$rest.se))) %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Variable = c("Intercept", 
                      "log(GDPpc)", 
                      "log(Older)",
                      "log(Density)",
                      "Transit",
                      "log(Humidity)",
                      "log(Temperature)",
                      rep(c("Intercept",
                            "log(Density)", 
                            "Transit", 
                            "log(Humidity)", 
                            "log(Temperature)"), 29)),
         Variable = factor(Variable, 
                           levels = c("Intercept", 
                                      "log(GDPpc)", 
                                      "log(Older)", 
                                      "log(Density)",
                                      "Transit", 
                                      "log(Humidity)",
                                      "log(Temperature)"))) %>%
  group_by(Variable) %>%
  summarize(Min = min(Coefficient), 
            Mean = mean(Coefficient), 
            Max = max(Coefficient),
            pns = sum(pval > 0.10), # Number of coefficients with p > 0.1
            p10 = sum(pval <= 0.10) - sum(pval <= 0.05), # Number of coefficients with  0.1 <= pval < 0.05
            p05 = sum(pval <= 0.05)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Non-constrained", 
                  "Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")) %>%
  kable("latex",
        #"html",
        booktabs = TRUE,
        digits = 3,
        col.names = c("Variable", "Min", "Mean", "Max", "p > 0.10", "0.10 <= p < 0.05", "p <= 0.05", "Note"),
        caption = "\\label{tab:summary-best-model}Summary of estimation results best model (lagged 11-day moving average)") %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  #kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  add_header_above(c(" " = 1, "Estimates" = 3, "Significance" = 3, " " = 1)) %>%
  footnote(general = c("Significance: This is the number of coefficients with p-values as indicated",
                       "Non-constrained: coefficient was allowed to vary across equations",
                       "Constrained: coefficient as constant across equations"))
```
